TacticToe: Learning the Game of Tactics

### 2018-01-28 tactictoe_jv.tex
predictions: almost done

\subsection{Similarity}\label{sec:predictions}
We estimate the similarity (or co-distance) between two objects $o_1$ and $o_2$ 
through their respective feature sets $f_1$ and $f_2$.
%The similarity function $sim$ computed by the k-NN algorithm is analogous 
%to the one used in the premise selection task~\cite{ckju-pxtp13}.
The estimation is based on the frequency of the features in the intersection of 
$f_1$ and $f_2$. A good rule of thumb is that the rarer the shared features 
are, the more similar two goals should be. This can be realized by 
calculating TF-IDF weights for each feature~\cite{Jones72astatistical}.
We additionally raise the weights to the sixth power giving even more credence 
to rare features which was found experimentally optimal in \cite{}.\todo{CK: 
citation}

@@

\begin{definition}(Dependencies of a theorem)\\
Let $\mathfrak{T}$ be the set of recorded theorems.
The dependencies $D_\infty$ of a theorem $t$ are the set of theorems in 
$\mathfrak{T}$ appearing in the proof $t$ as recorded in \cite{hh4h4}.
Contrarily to the dependency relation in tactic-goal pairs, this relation is 
not a transitive closure.
\end{definition}

>>>>

\subsection{Similarity}\label{sec:predictions}
We estimate the similarity (or co-distance) between two objects $o_1$ and $o_2$ 
through their respective feature sets $f_1$ and $f_2$.
%The similarity function $sim$ computed by the k-NN algorithm is analogous 
%to the one used in the premise selection task~\cite{ckju-pxtp13}.
The estimation is based on the frequency of the features in the intersection of 
$f_1$ and $f_2$. A good rule of thumb is that the rarer the shared features 
are, the more similar two goals should be. The relative rarity of each feature 
can be estimated by calculating its TF-IDF weight~\cite{Jones72astatistical}.
We additionally raise the weights to the sixth power giving even more credence 
to rare features which was found experimentally optimal in \cite{}.\todo{CK: 
citation}

@@

\begin{definition}(Dependencies of a theorem)\\
Let $\mathfrak{T}$ be the set of recorded theorems.
The dependencies of a theorem $t$ are the set of theorems in 
$\mathfrak{T}$ appearing in the proof of $t$ as recorded in 
\cite{hh4h4}.\todo{cite}
Contrarily to the dependency relation in tactic-goal pairs, this relation is 
not a transitive closure.
\end{definition}
